Quantum Hoare Type Theory

### 2020-11-11 ms-paper/ms-paper.tex
Move examples to individual files and switch to unicode literal chars

\usepackage{listings}
\lstloadlanguages{Haskell}
\lstdefinelanguage{QHaskell}{
	language     = Haskell,
	morekeywords = {Qbit, U, C, meas, apply, to},
}

\lstset{
	basicstyle=\small\ttfamily,
	flexiblecolumns=false,
	basewidth={0.5em,0.45em},
	commentstyle=\color{dkgreen},
	keywordstyle=\bfseries\color{blue},
	stringstyle=\color{violet},
	literate={+}{{$+$}}1 {/}{{$/$}}1 {*}{{$*$}}1 {=}{{$=$}}1
	{>}{{$>$}}1 {<}{{$<$}}1 {\\}{{$\lambda$}}1
	{\\\\}{{\char`\\\char`\\}}1
	{->}{{$\rightarrow$}}2 {>=}{{$\geq$}}2 {<-}{{$\leftarrow$}}2
	{<=}{{$\Leftarrow$}}2 {=>}{{$\Rightarrow$}}2
	{\ .}{{$\circ$}}2 {\ .\ }{{$\circ$}}2
	{>>}{{>>}}2 {>>=}{{>>=}}2
	{|}{{$\vert$}}1 {\\>}{{$\rangle$}}1
	{/\\}{{$\wedge$}}1 {\\/}{{$\vee$}}1
	{\\in}{{$\in$}}1 {\\o}{{$\circ$}}1 {\\Pi}{{$\Pi$}}1
	{\\Phi+}{{$\Phi^+$}}2
	{|->}{{$\mapsto$}}2 {-o}{{$\multimap$}}2
	{o*}{{$\otimes$}}1
	{\\top}{{$\top$}}1
	{\\bot}{{$\bot$}}1
	{=q}{{$=_q$}}2
	{alpha}{{$\alpha$}}1 {beta}{{$\beta$}}1
}

@@

\begin{figure}[ht]
	\begin{tabular}{lrcl}
		\textit{Types} & $A, B, C$ & ::= &
		\begin{minipage}[t]{0.45\columnwidth}%
			$ \type{1} \mid \type{Bool} \mid \type{Qbit} \mid A \otimes B \mid \Pi x{ : }A.B \mid \Delta. \Psi .\{P\} x{ : }A \{Q\}$
		\end{minipage}\\ \\
		\textit{Propositions} & $P, Q, R$ & ::= &
		\begin{minipage}[t]{0.5\columnwidth}%
			$ \top \mid \bot \mid P \wedge Q \mid P \vee Q \mid U \cdot P \mid \textbf{X} =_q \psi \mid \kw{uniform}(\textbf{X}) \mid \kw{separable}(\textbf{X}) \mid \kw{class}(\textbf{X}) $
		\end{minipage}\\ \\
		% \textit{Q. Heaps} & $H, G$ & ::= & $ h \mid \kw{empty} \mid \kw{upd}(H, M, N) $\\ \\
		\textit{Elim terms} & $K, L$ & ::= & $ x \mid K N \mid N : A $\\
		\textit{Intro terms} & $N, O$ & ::= & $ K \mid () \mid \lambda x.N \mid \kw{do} E \mid \kw{true} \mid \kw{false} $\\ \\
		\textit{Q. Commands} & $c$ & ::= &
		\begin{minipage}[t]{0.5\columnwidth}%
			$ \kw{\textbf{init}} N \mid \kw{\textbf{apply}} U \kw{\textbf{to}} N \mid \kw{\textbf{meas}} N$
		\end{minipage}\\
		\textit{Computations} & $E, F$ & ::= & $ \kw{return} N \mid x \leftarrow K; E \mid x \Leftarrow c; E \mid x = N; E $\\ \\
		\textit{Variable context} & $\Delta$ & ::= & $ \cdot \mid x : A, \Delta $ \\
		\textit{Q. Heap context} & $\Psi$ & ::= & $ \cdot \mid h, \Psi$ \\
		\textit{Proposition context} & $\Gamma$ & ::= & $ \cdot \mid P, \Gamma$ \\
		\textit{Unitaries} & $U$ & ::= & $ I \mid X \mid Y \mid Z \mid H \mid CX \mid CZ \mid S \mid T$
	\end{tabular}
	\Description{Syntax of Quantum Hoare Type Theory}
	\caption{Syntax of Quantum Hoare Type Theory}
	\label{fig:syntax}
\end{figure}

@@

There are other propositions that involve ghosts:
\begin{itemize}
	\item uniform(\textbf{X}) is an abbreviation for $(\textbf{X}, \textbf{e}) = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11})$ where \textbf{e} is  a fresh entangled ghost variable. It means that X is uniformly distributed.
	\item separable(\textbf{X}) is an abbreviation for $\textbf{X} \equiv_{q} \textbf{u}$ where \textbf{u} is a fresh unentangled ghost variable.
	\item class(\textbf{X}) is an abbreviation for $\textbf{X} \equiv_{cl} \textbf{u}$ where \textbf{u} is a fresh unentangled ghost variable. The classical equality symbol means that the variables on both side will measure to be the exact same value. That is, there is no superposition involved.
\end{itemize}

@@

We use the terms quantum state and quantum heaps interchangeably throughout. A quantum heap is a partial function from qubits (that can in turn be thought of as locations, represented using natural numbers) to at most one quantum state vector.

@@

\paragraph{Quantum Commands}
These are the quantum-specific effectful commands inspired by QIO for initialization, unitary application and measurement of qubits.
\texttt{init} $N$ initializes a given variable based on the value of the expression $N$ (typically \ket{0} or \ket{1} if N is a boolean).
\texttt{apply} $U$ \texttt{to} $X$ applies unitary operation $U$ to variables $X$.
\texttt{meas} $x$ measures the variable $x$ in the computational basis.
%\texttt{if y then E else F} executes computation $E$ if measuring variable $y$ returns 1 else executes $F$.

@@

\begin{mathpar}
	\inferrule
	{\Delta \vdash N \chk \type{Bool}
		\\ \Delta, x : \type{Qbit}; P \circ (x =_q \mathit{bool2ket}(N)) \vdash E \syn y:B . Q}
	{\Delta; P \vdash x \Leftarrow \kw{init} N; E \syn y:B. (\exists x:\type{Qbit}.Q)}
\end{mathpar}
where x is fresh.

Initialization can only be performed for a term $N$ that can be type checked as a \type{Bool}. Then, we look at the rest of the computation, $E$, in a context that adds $x$ of type \type{Qbit} under a precondition that extends the previous precondition, $P$, with the strongest postcondition for initialization, that is, the newly bound variable $x$ is equal to the \ket{0} or \ket{1}; this should synthesize the strongest postcondition (with respect to the expanded precondition in the context), $Q$, for $E$.

@@

\begin{mathpar}
	\inferrule
	{\Delta \vdash N \chk \type{Qbit}
		\\ \Delta; \Psi; P \prove (N =_q -)
		\\ \Delta, x:\type{Bool}; P \circ ((N =_q -) \multimap \top) \vdash E \syn y:B . Q}
	{\Delta; P \vdash x \Leftarrow \kw{meas} N; E \syn y:B. (\exists x:\type{Bool}.Q)}
\end{mathpar}

@@

\begin{minipage}{0.95\linewidth}
\begin{lstlisting}[language=QHaskell]
hqw : {\top} r : Bool {\top /\ r = false}
    = do q <= init false;
         r = meas q;
         return r
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{0.95\linewidth}
\begin{lstlisting}[language=QHaskell]
hqw : {\top} r : Bool {\top /\ r = false}
         -- \top
    = do q <= init false;
         -- q =q |0\> /\ class(q)
         r = meas q;
         -- (q, e) =q |00\> /\ r = false -- could use a sugared version for measured
         return r
         -- r = false -- if no qubit left, should be able to switch to \top here
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{0.95\linewidth}
\begin{lstlisting}[language=QHaskell]
rnd : {\top} r : Bool {\top}
    = do q <= init false;
         apply H to q;
         r = meas q;
         return r
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{0.95\linewidth}
\begin{lstlisting}[language=QHaskell]
rnd : {\top} r : Bool {\top}
         -- \top
    = do q <= init false;
         -- q =q |0\> /\ class(q)
         apply H to q;
         -- q =q |+\> /\ uniform(q)
         r = meas q;
         -- (q, e) =q |++\> -- perhaps we should be able to say uniform(r)?
         return r
         -- r = false \/ r = true -- or left unspecified
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{0.95\linewidth}
\begin{lstlisting}[language=QHaskell]
testBell00 : {\top} (a, b) : (Bool o* Bool) {\top /\ a = b}
         = do qa <= init false;
              apply H to qa;
              qb <= init false;
              <= apply CNOT to (qa, qb);
              a = meas qa;
              b = meas qb;
              return (a, b)
\end{lstlisting}
\end{minipage}

@@

\begin{lstlisting}[language=QHaskell]
testBell00 : {\top} (a, b) : (Bool o* Bool) {\top /\ a = b}
              -- \top
         = do qa <= init false;
              -- qa =q |0\>, class(qa)
              apply H to qa;
              -- qa =q |+\>, uniform(qa)
              qb <= init false;
              -- qa =q |+\>, uniform(qa), qb =q |0\>, class(qb)
              apply CNOT to (qa, qb);
              -- (qa, qb) =q |++\>  -- can use a weaker but more general `EPR' here
              -- /\ uniform(qa, qb) -- this won't apply then
              a = meas qa;
              --   (qa, e1) =q |00\>, (qb, e2) =q |00\>, a = false
              -- \/ (qa, e1) =q |11\>, (qb, e2) =q |11\>, a = true
              b = meas qb;
              --   (qa, e1) =q |00\>, (qb, e2) =q |00\>, a = false, b = false
              -- \/ (qa, e1) =q |11\>, (qb, e2) =q |11\>, a = true,  b = true
              return (a, b)
\end{lstlisting}

In the proposition P2, we show that only the portion of the quantum state referred to by the \texttt{apply} command is affected. Similarly, in P4 we see that only the relevant portion of the heap containing the control and target qubits used in the CNOT operation are affected. In this case, we also needed to combine the two qubit state as they are now entangled. The last proposition, P5, merely encodes the strongest postcondition for measurement for each of the two qubits.

@@

\begin{lstlisting}[language=QHaskell]
entangle-disentangle : {T} (a, b) : (Qbit o* Qbit) {a = b}
= do
    -- P0: T
    a <= init false;
    -- P1: a =q |0\>, class(a)
    b <= init false;
    -- P2: P1, b =q |0\>, class(b)
    apply H to a;
    -- P3: H_a.P2     =   a =q |+\>, b =q |0\>, uniform(a), class(b)
    apply CX to (a, b);
    -- P4: CX_ab.P3   =   (a, b) =q |++\>, uniform(a, b)
    apply CX to (a, b);
    -- P5: CX_ab.P4   =   (a =q |+\>, b =q |0\>) \/ (a =q |0\>, b =q |+\>)
    apply H to a;
    -- P6: H_a.P5     =   (a =q |0\>, b =q |0\>) \/ (a =q |+\>, b =q |+\>)
    return (a, b)
\end{lstlisting}

@@

\begin{turn}{90}
	\begin{minipage}{42pc}
	\begin{mathpar}
		\inferrule*[right=HIntro]
		{\inferrule*[right=consq]
			{\inferrule*[right=init]
				{\inferrule*[right=measure]
					{\inferrule*[right=return]
						{q : \type{Qbit}, r : \type{Bool} \vdash r \chk \type{Bool}}
						{q : \type{Qbit}, r : \type{Bool}; P_1 \circ ((q \mapsto -) \multimap \top) \vdash \kw{return} r \syn r : \type{Bool} . R}
						\\ q : \type{Qbit} \vdash q \chk \type{Qbit}
						\\ \cdot; P_0 * (q \mapsto \ket{0}) \prove (q \hookrightarrow -)
					}
					{q : \type{Qbit}; P_0 * (q \mapsto \ket{0}) \vdash r \Leftarrow \kw{meas} q; E_3 \syn r : \type{Bool} . (\exists r : \type{Bool}.R)}
					\\ \cdot \vdash \kw{0} \chk \type{Bool}
				}
				{
					\cdot; P_0 \vdash q \Leftarrow \kw{init false}; E_{23} \syn r : \type{Bool} . (\exists q : \type{Qbit}.R)
				}
				\\ r : \type{Bool}; i,m ; R \prove \top \multimap \top \wedge Id(r, \kw{0})
			}
			{
				\cdot; \lambda i . \lambda m . i = m \wedge (\top * \lambda m' \top)m \vdash E_1; E_{23} \chk r : \type{Bool} . (\top \multimap \top \wedge Id(r, \kw{0}))
			}
		}
		{\cdot \vdash \kw{do} E \chk \{\top\} r : \type{Bool} \{\top \wedge \kw{Id}(r, \kw{0})\}}
	\end{mathpar}
	\end{minipage}
\end{turn}

@@

\subsection{Hadamard basis states}
\begin{lstlisting}[language=QHaskell]
qplus : {\top} r : Qbit {r =q |+\>}
      = do q <= init false;
           q <= apply H to q;
           return q

qminus : {\top} r : Qbit {r =q |-\>}
       = do q <= init true;
            q <= apply H to q;
            return q
\end{lstlisting}

\subsection{Creating entanglement}
\begin{lstlisting}[language=QHaskell]
share : \Pi a : Qbit.
        {a =q (alpha |0\> + beta |1\>)}
           (a, b) : (Qbit o* Qbit)
        {(a, b) =q (alpha |00\> + beta |11\>)}
      = \a.do b <= init false;
              (a, b) <= apply CNot to [a, b];
              return (a, b)
\end{lstlisting}

\subsection{Bell pair}
\begin{lstlisting}[language=QHaskell]
bell00 : {\top} (a, b) : (Qbit o* Qbit) {(a,b) =q |\Phi+\>}
     = do qa <- qplus;
          (qa, qb) <- share qa;
          return (qa, qb)
\end{lstlisting}

\subsection{Testing modular Bell pair}
\begin{lstlisting}[language=QHaskell]
testBell : {\top} (a, b) : (Bool o* Bool) {\top /\ a = b}
         = do (qa, qb) <- bell00;
              a <= meas qa;
              b <= meas qb;
              return (a, b)
\end{lstlisting}

\section{Teleportation}
\label{app:teleport}
\subsection{Alice's circuit}
\begin{lstlisting}[language=QHaskell]
alice : \Pi q : Qbit. \Pi a : Qbit
        {q =q (alpha |0\> + beta |1\>) /\ (a, e) =q |\Phi+\>}    -- a is entangled with ghost var e
           (m1, m2) : (Bool o* Bool)
        {  (m1, m2) = 00 /\ e =q (alpha |0\> + beta |1\>)
         \/ (m1, m2) = 01 /\ e =q (alpha |1\> + beta |0\>)
         \/ (m1, m2) = 10 /\ e =q (alpha |0\> - beta |1\>)
         \/ (m1, m2) = 11 /\ e =q (alpha |1\> - beta |0\>)}
      = \q.\a.do (q, a) <= apply CNOT to [q, a];
                 q <= apply H to q;
                 rq <= meas q;
                 ra <= meas a;
                 return (rq, ra)
\end{lstlisting}

\subsection{Bob's circuit}
\todo{TODO provide correct propositions using ghost e}
\begin{lstlisting}[language=QHaskell]
bob : \Pi m1 m2 : Bool. \Pi b : Qbit
      {(b, e) =q |\Phi+\>}
         r : Qbit
      {\top}
      = \m1.\m2.\b.do (m1, b) <= apply C_Z to [m1, b];
                      (m2, b) <= apply C_X to [m2, b];
                      return b
\end{lstlisting}

\subsection{Teleport}
\begin{lstlisting}[language=QHaskell]
teleport : \Pi q : Qbit.
           {q =q (alpha |0\> + beta |1\>)}
              b : Qbit
           {r =q (alpha |0\> + beta |1\>)}
         = \q.do (a, b) <- bell00;
                 (m1, m2) <- alice q a;
                 b <- bob m1 m2 b;
                 return b
\end{lstlisting}

>>>>

\usepackage{listings}
\lstloadlanguages{Haskell}
\lstdefinelanguage{QHaskell}{
	language     = Haskell,
	morekeywords = {bool, qbit, U, C, meas, apply, to},
}

\lstset{
	basicstyle=\small\ttfamily,
	flexiblecolumns=false,
	basewidth={0.5em,0.45em},
	commentstyle=\color{dkgreen},
	keywordstyle=\bfseries\color{blue},
	stringstyle=\color{violet},
	literate={+}{{$+$}}1 {/}{{$/$}}1 {*}{{$*$}}1 {=}{{$=$}}1
	{√}{{$\surd$}}1
	{>}{{$>$}}1 {<}{{$<$}}1 {λ}{{$\lambda$}}1
	{\\\\}{{\char`\\\char`\\}}1
	{⇐}{{$\Leftarrow$}}1 {⇒}{{$\Rightarrow$}}2
	{\ .}{{$\circ$}}2 {\ .\ }{{$\circ$}}2
	{|}{{$\vert$}}1 {⟩}{{$\rangle$}}1
	{∧}{{$\wedge$}}1 {∨}{{$\vee$}}1
	{∈}{{$\in$}}1 {Π}{{$\Pi$}}1
	{⊗}{{$\otimes$}}1
	{⊤}{{$\top$}}1
	{=q}{{$=_q$}}2 {=c}{{$=_c$}}2
	{α}{{$\alpha$}}1 {β}{{$\beta$}}1
}

@@

\begin{figure}[ht]
	\begin{tabular}{lrcl}
		\textit{Types} & $A, B, C$ & ::= &
		\begin{minipage}[t]{0.6\columnwidth}%
			$ \type{unit} \mid \type{bool} \mid \type{prop} \mid \type{qbit} \mid A \otimes B \mid \Pi x{ : }A.B \mid \{P\} x{ : }A \{Q\}$
		\end{minipage}\\ \\
		\textit{Propositions} & $P, Q, R$ & ::= &
		\begin{minipage}[t]{0.6\columnwidth}%
			$ \top \mid \bot \mid P \wedge Q \mid P \vee Q \mid \neg P \mid U \cdot P \mid \textbf{X} =_q \psi$
		\end{minipage}\\ \\
		% \textit{Q. Heaps} & $H, G$ & ::= & $ h \mid \kw{empty} \mid \kw{upd}(H, M, N) $\\ \\
		\textit{Elim terms} & $K, L$ & ::= & $ x \mid \kw{fst} K \mid \kw{snd} K \mid K\ N \mid M : A $\\
		\textit{Intro terms} & $M, N, O$ & ::= & $ K \mid () \mid \kw{true} \mid \kw{false} \mid (M, N) \mid \lambda x.M \mid \kw{do} E$\\ \\
		\textit{Unitaries} & $U$ & ::= & $ I \mid X \mid Y \mid Z \mid H \mid CX \mid CZ \mid S$\\
		\textit{Q. Commands} & $c$ & ::= &
		\begin{minipage}[t]{0.6\columnwidth}%
			$ \kw{init} N \mid \kw{apply} U \kw{to} N \mid \kw{meas} N \mid
			\kw{if} M \kw{then} E \kw{else} F$
		\end{minipage}\\
		\textit{Computations} & $E, F$ & ::= & $ \kw{return} N \mid \kw{run} x = K \kw{in} E \mid x = c; E \mid x = N; E $\\ \\
		\textit{Context} & $\Delta$ & ::= & $ \cdot \mid x : A, P, \Delta $ \\
%		\textit{Q. Heap context} & $\Psi$ & ::= & $ \cdot \mid h, \Psi$ \\
%		\textit{Proposition context} & $\Gamma$ & ::= & $ \cdot \mid P, \Gamma$ \\

	\end{tabular}
	\Description{Syntax of Quantum Hoare Type Theory}
	\caption{Syntax of Quantum Hoare Type Theory}
	\label{fig:syntax}
\end{figure}

@@

@@

\todo{TODO}

%We use the terms quantum state and quantum heaps interchangeably throughout. A quantum heap is a partial function from qubits (that can in turn be thought of as locations, represented using natural numbers) to at most one quantum state vector.

@@

\paragraph{Quantum Commands}
These are the quantum-specific effectful commands inspired by QIO for initialization, unitary application and measurement of qubits.
\texttt{init} $N$ initializes a given variable based on the value of the expression $N$ (typically \ket{0} or \ket{1} if N is a boolean).
\texttt{apply} $U$ \texttt{to} $X$ applies unitary operation $U$ to variables $X$.
\texttt{meas} $x$ measures the variable $x$ in the computational basis and returns a classical result.
\texttt{if y then E else F} executes computation $E$ if measuring variable $y$ returns 1 else executes $F$.

@@

\begin{mathpar}
	\inferrule
	{\Delta \vdash N \chk \type{bool}
		\\ \Delta, x : \type{qbit}; P \circ (x =_q \mathit{bool2ket}(N)) \vdash E \syn y:B . Q}
	{\Delta; P \vdash x \Leftarrow \kw{init} N; E \syn y:B. (\exists x:\type{qbit}.Q)}
\end{mathpar}
where x is fresh.

Initialization can only be performed for a term $N$ that can be type checked as a \type{bool}. Then, we look at the rest of the computation, $E$, in a context that adds $x$ of type \type{qbit} under a precondition that extends the previous precondition, $P$, with the strongest postcondition for initialization, that is, the newly bound variable $x$ is equal to the \ket{0} or \ket{1}; this should synthesize the strongest postcondition (with respect to the expanded precondition in the context), $Q$, for $E$.

@@

\begin{mathpar}
	\inferrule
	{\Delta \vdash N \chk \type{qbit}
		\\ \Delta; \Psi; P \prove (N =_q -)
		\\ \Delta, x:\type{bool}; P \circ ((N =_q -) \multimap \top) \vdash E \syn y:B . Q}
	{\Delta; P \vdash x \Leftarrow \kw{meas} N; E \syn y:B. (\exists x:\type{bool}.Q)}
\end{mathpar}

@@

\begin{minipage}{0.95\linewidth}
\lstinputlisting[language=QHaskell,lastline=4]{hqw.qh}
\end{minipage}

@@

\begin{minipage}{0.95\linewidth}
\lstinputlisting[language=QHaskell,firstline=6]{hqw.qh}
\end{minipage}

@@

\begin{minipage}{0.95\linewidth}
\lstinputlisting[language=QHaskell,lastline=5]{toss.qh}
\end{minipage}

@@

\begin{minipage}{0.95\linewidth}
\lstinputlisting[language=QHaskell,firstline=7]{toss.qh}
\end{minipage}

@@

\begin{minipage}{0.95\linewidth}
\lstinputlisting[language=QHaskell,lastline=8]{bell.qh}
\end{minipage}

@@

\lstinputlisting[language=QHaskell,firstline=10]{bell.qh}

In the proposition P2, we show that only the portion of the quantum state referred to by the \texttt{apply} command is affected. Similarly, in P4 we see that only the relevant portion of the heap containing the control and target qubits used in the CX operation are affected. In this case, we also needed to combine the two qubit state as they are now entangled. The last proposition, P5, merely encodes the strongest postcondition for measurement for each of the two qubits.

@@

\lstinputlisting[language=QHaskell]{entdisent.qh}

@@

\begin{turn}{90}
	\begin{minipage}{42pc}
	\begin{mathpar}
		\inferrule*[right=HIntro]
		{\inferrule*[right=consq]
			{\inferrule*[right=init]
				{\inferrule*[right=measure]
					{\inferrule*[right=return]
						{q : \type{qbit}, r : \type{bool} \vdash r \chk \type{bool}}
						{q : \type{qbit}, r : \type{bool}; P_1 \circ ((q \mapsto -) \multimap \top) \vdash \kw{return} r \syn r : \type{bool} . R}
						\\ q : \type{qbit} \vdash q \chk \type{qbit}
						\\ \cdot; P_0 * (q \mapsto \ket{0}) \prove (q \hookrightarrow -)
					}
					{q : \type{qbit}; P_0 * (q \mapsto \ket{0}) \vdash r \Leftarrow \kw{meas} q; E_3 \syn r : \type{bool} . (\exists r : \type{bool}.R)}
					\\ \cdot \vdash \kw{0} \chk \type{bool}
				}
				{
					\cdot; P_0 \vdash q \Leftarrow \kw{init false}; E_{23} \syn r : \type{bool} . (\exists q : \type{qbit}.R)
				}
				\\ r : \type{bool}; i,m ; R \prove \top \multimap \top \wedge Id(r, \kw{0})
			}
			{
				\cdot; \lambda i . \lambda m . i = m \wedge (\top * \lambda m' \top)m \vdash E_1; E_{23} \chk r : \type{bool} . (\top \multimap \top \wedge Id(r, \kw{0}))
			}
		}
		{\cdot \vdash \kw{do} E \chk \{\top\} r : \type{bool} \{\top \wedge \kw{Id}(r, \kw{0})\}}
	\end{mathpar}
	\end{minipage}
\end{turn}

@@

\subsection{Hadamard basis states}
\lstinputlisting[language=QHaskell]{hadbasis.qh}

\subsection{Creating entanglement}
\lstinputlisting[language=QHaskell]{share.qh}

\subsection{Bell pair}
\lstinputlisting[language=QHaskell]{bell00.qh}

\subsection{Testing modular Bell pair}
\lstinputlisting[language=QHaskell]{testbell.qh}

\section{Teleportation}
\label{app:teleport}
\subsection{Alice's circuit}
\lstinputlisting[language=QHaskell,lastline=12]{teleport.qh}

\subsection{Bob's circuit}
\todo{TODO provide correct propositions using ghost e}
\lstinputlisting[language=QHaskell,firstline=14,lastline=20]{teleport.qh}

\subsection{Teleport}
\lstinputlisting[language=QHaskell,firstline=22]{teleport.qh}
